
## Module 01: {-}


```{r, eval=TRUE}
txt_styling = function(htmlText, htmlDisplayColor){
  paste0("<span style='color:", htmlDisplayColor, ";font-weight:bold'>", htmlText, "</span>")
}
```

```{r, eval=TRUE}
leafType = function(text, textColor){
  paste0( txt_styling(text, textColor) )
}
```

```{r, eval=TRUE}
theory_todo = function(){
  paste0(leafType("Theory", "red"))
}
```

```{r, eval=TRUE}
theory_complete = function(){
  paste0(leafType("Theory", "green"))
}
```

```{r, eval=TRUE}
example_todo = function(){
  paste0(leafType("Example", "red"))
}
```

```{r, eval=TRUE}
example_complete = function(){
  paste0(leafType("Example", "green"))
}
```

```{r, eval=TRUE}
description_todo = function(){
  paste0(leafType("Description", "red"))
}
```

```{r, eval=TRUE}
description_complete = function(){
  paste0(leafType("Description", "green"))
}
```

```{r, eval=TRUE}
code_todo = function(){
  paste0(leafType("Code", "red"))
}
```

```{r, eval=TRUE}
code_complete = function(){
  paste0(leafType("Code", "green"))
}
```

```{r, eval=TRUE}
exercise_todo = function(){
  paste0(leafType("Excercise", "red"))
}
```

```{r, eval=TRUE}
exercise_complete = function(){
  paste0(leafType("Excercise", "green"))
}
```

1. `r theory_todo()`   
Overview of Kafka.


1. `r example_todo()`   
Detailed Overview of Kafka.
    - `r description_complete()`
    - `r code_todo()`



1. `r example_todo()`   
Detailed Overview of Kafka.
    - `r description_todo()`
    - `r code_complete()`

1. `r theory_complete()`   
Overview of Kafka.

1. `r exercise_todo()`   
Detailed Overview of Kafka.
    - `r description_todo()`
    - `r code_complete()`
    
1. `r exercise_complete()`   
Detailed Overview of Kafka.
    - `r description_todo()`
    - `r code_complete()`    



